Web Processing - Standardised GIS Analyses for Cable Route Planning

### 2023-01-11 paper/paper-CableRoute.tex
updated paper:
minor fixes

\documentclass[acmtog]{acmart}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{subfig}
\usepackage[acronym]{glossaries}
\usepackage{todonotes}
\usepackage{tikz}

@@

	Hence, the mean minimum euclidean distance between the two paths can used to compute
	the similarity.
	As different table~\ref{table:2} shows the distance between the two paths decreases
	with increasing resolution. In addition, this tendency is depicted in figure~\ref{fig:paths_alltouched} for the calculated cost paths of 5m and 100 m resolutions.

@@

	\begin{table*}[t]
	\caption{Least cost paths as length for the different \acrfull{res} of the rasters, including the \acrfull{mmd} and the \acrfull{agg} costs. From the \acrshort{agg} costs the differences of the \acrshort{agg} costs and the \acrfull{corr} \acrshort{agg} by resolution are given.} 
	\label{table:2}
	\centering
	\begin{tabular}{ r  r  r  r  r  r  r  r  r}
		\acrshort{res} /m & $length_{\acrshort{al}=\acrshort{f}} /m$ & $length_{\acrshort{al}=\acrshort{t}} /m$ & \acrshort{mmd} /m & \acrshort{agg}  $ cost_{\acrshort{al}=\acrshort{f}}$ & \acrshort{agg}  $ cost_{\acrshort{al}=\acrshort{t}}$ &  $\Delta $ costs & \acrshort{corr} \acrshort{agg} $costs_{\acrshort{al}=\acrshort{f}}$ & \acrshort{corr} \acrshort{agg} $costs_{\acrshort{al}=\acrshort{t}} $ \\
		\hline
		5 & 76136.27	& 78002.00 & 126.04  & 18665.923 & 19616.756 & -850 & 93329.6 &  97584.77 \\
		10 & 75430.10 	& 77936.57 & 277.92 & 8931.245 & 9731.175 & -799.95 & 89312.45 & 97311.75 \\
		50 & 76135.02	& 70619,95 & 1140.01 & 1409.023 & 2300.073 & -891.05 & 70451.15 & 115003.65 \\
		100 & 76283.80	& 74120.73 & 1946.41 & 640.516 & 1572.268 & -931.7 & 64051.6 & 167226.8 \\

@@

	\section{Discussion}
	\todo{discuss aggregation with max vs sum}
	\todo{discuss other methods. Off algorithmic speed-ups}
	\todo{discuss other technical methods of speed-ups, as precompilation, JIT, vector units, multi-core}
	\section{Related Works}
	\section{Conclusion}

>>>>

\documentclass[acmtog]{acmart}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{subfig}
\usepackage[acronym]{glossaries}
\usepackage{todonotes}
\usepackage{tikz}
\usepackage{graphicx}

@@

	Hence, the mean minimum euclidean distance between the two paths can used to compute
	the similarity.
	As different table~\ref{tab:2} shows the distance between the two paths decreases
	with increasing resolution.
	In addition, this tendency is depicted in figure~\ref{fig:paths_resolution} for the calculated cost paths of 5m and 100 m resolutions.

@@

	\begin{table*}[t]
	\caption{Least cost paths as length for the different \acrfull{res} of the rasters, including the \acrfull{mmd} and the \acrfull{agg} costs. From the \acrshort{agg} costs the differences of the \acrshort{agg} costs and the \acrfull{corr} \acrshort{agg} by resolution are given.} 
	\label{tab:2}
	\centering
	\begin{tabular}{ r  r  r  r  r  r  r  r  r}
		\acrshort{res} /m & $length_{\acrshort{al}=\acrshort{f}} /m$ & $length_{\acrshort{al}=\acrshort{t}} /m$ & \acrshort{mmd} /m & \acrshort{agg}  $ cost_{\acrshort{al}=\acrshort{f}}$ & \acrshort{agg}  $ cost_{\acrshort{al}=\acrshort{t}}$ &  $\Delta $ costs & \acrshort{corr} \acrshort{agg} $costs_{\acrshort{al}=\acrshort{f}}$ & \acrshort{corr} \acrshort{agg} $costs_{\acrshort{al}=\acrshort{t}} $ \\
		\hline
		5 & 76136.27	& 78002.00 & 126.04  & 18665.923 & 19616.756 & -850 & 93329.6 &  97584.77 \\
		10 & 75430.10 	& 77936.57 & 277.92 & 8931.245 & 9731.175 & -799.95 & 89312.45 & 97311.75 \\
		50 & 76135.02	& 70619,95 & 1140.01 & 1409.023 & 2300.073 & -891.05 & 70451.15 & 115003.65 \\
		100 & 76283.80	& 74120.73 & 1946.41 & 640.516 & 1572.268 & -931.7 & 64051.6 & 167226.8 \\

@@

	\section{Discussion}
	\todo{discuss aggregation with max vs sum}
	\todo{Scaling with multiple endpoints.}
	\todo{discuss other methods. Off algorithmic speed-ups}
	\todo{discuss other technical methods of speed-ups, as precompilation, JIT, vector units, multi-core}
	\section{Related Works}
	\section{Conclusion}
